Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-06 draft.tex
merge

\begin{prp}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible $\PP_0$-factorization algebra 
\begin{equation}\label{eqn:graded}
\left(\Tilde{\bZ}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
\end{equation}
on $M \times \RR_{\geq 0}$ such that $\pi_* \Tilde{\bZ}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection. 
\end{prp}

@@

@@

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as ``topological BF theory". 
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
In the BV formalism, the perturbative space of fields of BF theory on $N$ consists of
\[
(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
\]
When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
It can be interpreted as the following mapping stack 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d_A B + [A,B] & = 0 .
\end{align*}

@@

\begin{prp}
The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n (\fg))$ of Definition \ref{dfn:constructible1}. 
\end{prp}
%\subsection{The bulk TFT}
%
%Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
%This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct. 
%
%\begin{dfn}
%For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
%\[
%\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
%\]
%The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
%\end{dfn}
%
%We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
%In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory". 
%
%We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
%Recall, this model is given by the factorization algebra on $M$:
%\begin{equation}\label{eqn:centerTFT}
%\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
%\end{equation}
%
%The ``dequantization" is defined using the following filtration of this model.
%For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
%
%\begin{dfn}
%Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
%\[
%F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
%\]
%\end{dfn}
%
%This is a filtration of factorization algebras on $M$. 
%The associated graded factorization algebra is
%\[
%{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
%\]
%Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
%
% \begin{lmm}
%There is a quasi-isomorphism of commutative factorization algebras on $M$:
%\[
%\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
%\]
%\end{lmm}
%
%In fact, we will show that this quasi-isomorphism is a deformation retraction. 
%
%\begin{proof}
%To exhibit this quasi-isomorphism, we introduce the following cochain maps.
%For an open set $U \subset M$ let
%\[
%\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
%\] 
%be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
%This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
%Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
%\[
%r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
%\]
%by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
%\end{proof}

>>>>

\begin{prp}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra 
\begin{equation}\label{eqn:graded}
\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
\end{equation}
on $M \times \RR_{\geq 0}$ such that $\pi_* {\bf Bulk}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection.

\brian{lifts to $\PP_0$}.
\end{prp}

@@

\begin{prp}
Filtered swiss cheese.
Gr is a P_0 swiss cheese algebra.
\end{prp}

@@

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as ``topological BF theory". 
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
In the BV formalism, the perturbative space of fields of BF theory on $N$ consists of
\[
(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
\]
When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
It can be interpreted as the following mapping stack 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d B + [A,B] & = 0 .
\end{align*}

@@

\begin{prp}
The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n (\fg))$ of Definition \ref{dfn:constructible1}. 
\end{prp}

\brian{spectral sequence}

%\subsection{The bulk TFT}
%
%Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
%This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct. 
%
%\begin{dfn}
%For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
%\[
%\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
%\]
%The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
%\end{dfn}
%
%We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
%In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory". 
%
%We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
%Recall, this model is given by the factorization algebra on $M$:
%\begin{equation}\label{eqn:centerTFT}
%\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
%\end{equation}
%
%The ``dequantization" is defined using the following filtration of this model.
%For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
%
%\begin{dfn}
%Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
%\[
%F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
%\]
%\end{dfn}
%
%This is a filtration of factorization algebras on $M$. 
%The associated graded factorization algebra is
%\[
%{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
%\]
%Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
%
% \begin{lmm}
%There is a quasi-isomorphism of commutative factorization algebras on $M$:
%\[
%\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
%\]
%\end{lmm}
%
%In fact, we will show that this quasi-isomorphism is a deformation retraction. 
%
%\begin{proof}
%To exhibit this quasi-isomorphism, we introduce the following cochain maps.
%For an open set $U \subset M$ let
%\[
%\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
%\] 
%be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
%This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
%Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
%\[
%r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
%\]
%by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
%\end{proof}
